Multiple imputation of incomplete multilevel data using Heckman selection models

### 2022-12-16 1.Paper/Paper.Rmd
Update Paper.Rmd

Further, the method can also be extended to other types of variables such as count or ordinal variables. Similarly, less restrictive Heckman based models can be considered in terms of normality distribution of errors and no specification of exclusion variables such as those proposed by Ogundimu & Collins (2019).[@ogundimu_collins19].

>>>>

Further, the method can also be extended to other copula models for non-random selection, with different distributions of the selection and outcome equations and dependency structure.[@wojtys2018]  Similarly, less restrictive Heckman based models can be considered in terms of normality distribution of errors and no specification of exclusion variables such as those proposed by Ogundimu & Collins (2019).[@ogundimu_collins19].
